```{r setup}
knitr::opts_chunk$set(cache = TRUE)
```

```{r}
load_libraries <- function() {
  library(readr)
  library(dplyr)
}
load_libraries()
```

```{r}
products <- read_csv("data/digikala-products.csv")
comments <- read_csv("data/digikala-comments.csv")
```

#### Products - rename columns 

```{r}
rename_columns <- function(df) {
  df %>%
    rename(
      rate = Rate,
      rate_cnt = Rate_cnt,
      category_1 = Category1,
      category_2 = Category2,
      brand = Brand,
      price = Price,
      seller = Seller,
      is_fake = Is_Fake
    )
}
products <- rename_columns(products)
```

#### Hmmm ...

```{r}
summary(products)
summary(comments)
```

##### Checking what each column is

```{r}
colnames(products)
colSums(is.na(products)) # seller nan, price 0
products$rate[1:10]
products$rate_cnt[1:100]
products$category_1 %>%
  unique() %>%
  head(50)
products$category_2 %>%
  unique() %>%
  head(20)
products %>%
  filter(category_1 == "بهداشت دهان و دندان") %>%
  arrange(price) # Category 2 is the subcategory
# prices are in RIAL
# Check 3552869 id in products and this link :
# https://www.digikala.com/product/dkp-3552869/%D9%85%D8%B3%D9%88%D8%A7%DA%A9-%D9%87%D8%A7%DB%8C%D8%AF%D9%86%D8%AA-%D9%85%D8%AF%D9%84-909-%D8%A8%D8%A7-%D8%A8%D8%B1%D8%B3-%D9%85%D8%AA%D9%88%D8%B3%D8%B7/
#
products$seller[1:10]
products$sub_category %>% unique() # very few
```

```{r}
colnames(comments)
comments$body[1:10] # comment text
comments$created_at[1:10] # needs parsing
comments %>%
  select(created_at) %>%
  unique() # contains 1399, 1400, 1401, 1402

comments$rate[1:50]
comments$recommendation_status %>% unique()
comments %>%
  count(is_buyer)
comments %>%
  filter(is_buyer == TRUE) %>%
  head(20)
comments$product_id[1:10]
comments$advantages[1:50]
comments$disadvantages[1:50]
comments$likes[1:50]
comments$seller_title[1:50]
comments %>%
  filter(product_id == 13287852)
comments$seller_code[1:10] # what is this?
comments$true_to_size_rate %>% unique() # is fit or not
```

## Ideas
### Predictions
#### Product Recommendation System
#### Sentiment Analysis of Comments
#### Product Rating Prediction
#### Price Optimization
#### Demand Forcasting
#### Product Similarity
#### Product Rating Lifecycle
#### Trends in Seasons
#### Automated Price Categorization Using NLP
#### Product Return Prediction
#### Product Being Fake Matters?
#### Similar Product Analysis
#### Historical Events Effect On Market
#### Outliers Analysis (in Product and Comments) (For Detecting Fraud)

### Financial
#### Price Elasticity of Demand
#### Analysis Of Stock Out
#### Products With High Return

### Marketing 
#### Customer Segmentation
#### Customer Retention Strategy
#### Create Product Bundle
#### Product Description Quality Analysis
#### Customer Churn Prediction
#### Seller Response Rate And Changes To Comments
#### Finding Topics Using Comments
#### Important Factors In a Good Product
#### Customer Journay

### Fraud Detection
#### Fake Product Detection
#### Spam Comments Detection
#### Review Evaluation System

### Credit Systems
#### Seller Reputation Analysis
#### Seller Performance Evaluation
